Finite Property Convex Elicitation Notes

### 2018-05-04 cvx-fin-notes.tex
more notes, and eureka moment for higher dimensions

\section{Finite 1-d case}

@@

\raf{I think what I tried to show below was the following; might only be true up to some technicalities.}
\begin{proposition}
  Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
\end{proposition}
\begin{proof}
  From Proposition~\ref{prop:fplc-trim-char}, it suffices to show that $\Gamma_L\cap\R'$ is orderable.
  \raf{I need to reference some other stuff above about $\trim(\Gamma_L)$.}
  Let $\R' = \{r_1,\ldots,r_m\}$ with $r_1 < \cdots < r_m$.
  Recalling the optimality condition for $r_i \in \Gamma_L(p)$ in eq.~\eqref{eq:1d-optimality}, we see that
  \begin{equation*}\label{eq:fplc-level-set}
    \Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot d^-(r_i) \leq 0 \leq p\cdot d^+(r_{i}) \}~.
  \end{equation*}
  Thus, observing that $d^+(r_i) = d^-(r_{i+1})$ from Lemma~\ref{lem:fplc-directional-deriv}, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot d^+(r_i) = 0\}$ is a hyperplane.
\end{proof}

\raf{I think this is even easier than what I tried to show below.}
\begin{proposition}
  A finite property is essentially convex elicitable in $1$ dimension if and only if it is orderable.
  Moreover, this remains true when restricting to piecewise linear loss functions.
\end{proposition}

\section{2-d case}
\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}

>>>>

\section{One dimension}

@@

\begin{corollary}\label{cor:fplc-orderable}
  Every FPLC $L : \reals \to \reals^\Y$ essentially elicits a finite orderable property.
\end{corollary}
\begin{proof}
  From Proposition~\ref{prop:fplc-trim-char}, it suffices to show that $\Gamma_L\cap\R'$ is orderable.
  \raf{I need to reference some other stuff above about $\trim(\Gamma_L)$.}
  Let $\R' = \{r_1,\ldots,r_m\}$ with $r_1 < \cdots < r_m$.
  Recalling the optimality condition for $r_i \in \Gamma_L(p)$ in eq.~\eqref{eq:1d-optimality}, we see that
  \begin{equation*}\label{eq:fplc-level-set}
    \Gamma_{r_i} = \{ p \in \Delta_\Y : p\cdot d^-(r_i) \leq 0 \leq p\cdot d^+(r_{i}) \}~.
  \end{equation*}
  Thus, observing that $d^+(r_i) = d^-(r_{i+1})$ from Lemma~\ref{lem:fplc-directional-deriv}, for all $i$ the intersection $\Gamma_{r_i} \cap \Gamma_{r_{i+1}} = \{ p \in \Delta_\Y : p\cdot d^+(r_i) = 0\}$ is a hyperplane.
\end{proof}

\begin{theorem}\label{thm:fplc-orderable}
  A finite property is essentially convex elicitable in $1$ dimension if and only if it is orderable.
  Moreover, this remains true when restricting to piecewise linear loss functions.
\end{theorem}
\begin{proof}
  From Corollary~\ref{cor:fplc-orderable}, it remains to show two things: (i) \raf{general convex losses}, and (ii) a finite ordeable property is elicitable by a FPLC loss function.  
\end{proof}

\section{General dimensions}

\begin{lemma}\label{lem:sum-fplc}
  The sum of FPLC functions $f_1,\ldots,f_k$ is itself FPLC.
\end{lemma}
\begin{proof}
  Math.
\end{proof}

\begin{proposition}\label{cor:fplc-finite}
  Every FPLC $L : \reals^d \to \reals^\Y$ essentially elicits a finite property.
\end{proposition}
\begin{proof}
  Let $f(r) = \sum_{y\in\Y} L(r)_y$ which is FPLC by Lemma~\ref{lem:sum-fplc}.
  \raf{Perhaps its worth getting into power diagrams here...}
  Let $\R$ be the vertices of the cell complex given by $f$, that is, the points at which $\dim\partial f(r) = d$.
  As $f$ is FPLC, $\R$ is finite.
  We claim that $L$ essentially elicits $\Gamma_L\cap\R$.

  \raf{Now we just need to show that every point *not* on a vertex is weakly dominated by a vertex.}
\end{proof}

\raf{I further conjecture that there is a convex subset $C$ of $\reals^d$ such that $\R' = \R\cap C$ gives $\trim(\Gamma_L) = \Gamma_L\cap \R'$, just like in the 1-d case.  If that's true, it would be really helpful in figuring out what the constraints are in the simplex between neighbering reports!}

\section{Jessie's notes}
\raf{... have got it growing oats?}

\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
